SunPy - Python for Solar Physics

### 2014-01-30 1-Introduction.tex
edit to introduction

The SunPy project aims to provide a free, open-source and openly developed 
software package for the analysis and visualisation of solar data. SunPy makes 
use of the Python programming language and scientific Python packages. Python 
is a general-purpose, powerful and easy-to-learn high-level programming 
language.
% RJH: Can we cut the next sentence?  It seems superfluous and top 10 is rather
% meaningless.
% schriste - i think it's important. it contrasts nicely with IDL and its tiny 
%community.
%SJM: I think it should stay, it makes a point.
According to the 2014 TIOBE 
Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
it is one of the top ten most popular programming languages in the world 
and is widely used outside of scientific fields in areas like web development, 
education and `big data' analytics.

>>>>

The SunPy project aims to provide a free, open-source and openly developed 
software package for the analysis and visualisation of solar data. SunPy makes 
use of the Python programming language and scientific Python packages. Python 
is a general-purpose, powerful and easy-to-learn high-level programming 
language.
% RJH: Can we cut the next sentence?  It seems superfluous and top 10 is rather
% meaningless.
% schriste - i think it's important. it contrasts nicely with IDL and its tiny 
%community.
%SJM: I think it should stay, it makes a point.
%According to the 2014 TIOBE 
%Index\footnote{\url{http://www.tiobe.com/index.php/content/paperinfo/tpci/index.html}},
%it is one of the top ten most popular programming languages in the world 
%removed until better reference is found for this statistic.
Python is widely used outside of scientific fields in areas like web development, 
education and `big data' analytics.
